An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-07-07 gas-adsorption/referee-response.md

## Response to referees

Dear editor,

Thank you so much for being so flexible with extensions to the deadline for our
paper revision.  We have made a few major changes in response in particular to
suggestions by referee 3 (see below).  The revised PDF has substantially
modified sections noted with a red bar in the margin, and a short red note
explaining what the change was.

### 2021-07-08 gas-adsorption/rsc-gas-ads-complete.tex
edits from jordan

\startreferees{Added discussion of screening studies}
Finally, a number of empirical studies have been performed that computationally
simulate a adsorption in a vast array of possible porous
structures~\cite{firlej2013understanding, goldsmith2013theoretical,
ahmed2019exceptional}.  Such studies can guide the development of new materials
by allowing researchers to identify commonalities among materials that have
desirable properties.  However, such an approach can only place a \emph{lower
bound} on the highest attainable deliverable capacity.

@@

\startreferees{Flexible MOFs section added below}
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{figs/two-phase}
    \caption{Cartoon of a two-phase, collapsing material. The material can exist in two phases: an open phase in which gas molecules can adsorb and a closed phase that is collapsed and cannot fit any gas molecules. Take the closed phase as more stable, so that the material can collapse and expels residual gas.
    The pressure of gas at which the structural transition occurs depends on the gas-host interactions and relative stability of the phases. We wish for the structural transition to occur between $\pfull$ and $\pempty$.
    }
    \label{fig:flexible-cartoon}
\end{figure}

@@

       comparison~\cite{fixme}, along with the free energy difference between open and closed conformations~\cite{fixthis}.}

@@

Figure~\ref{fig:methane-flexible} illustrates
how the upper bound on the deliverable capacity of methane in a two-phase,
collapsing material depends on $\Delta F$. 
For comparison, we include the free energy
difference for Co(bdp)~\davidsays{CITE} and its measured deliverable capacity.  
While this upper bound is not rigorous, it suggests that a two-phase flexible material for methane storage
would benefit from significantly greater stability of the closed phase---provided the open phase
had correspondingly greater attraction for the gas molecules.  Figure~\ref{fig:hydrogen-flexible}
shows the corresponding result for hydrogen storage, indicating that, for a flexible material to
reach the DOE ULTIMATE deliverable capacity, it would require far greater stability for the closed
phase, as well as an unprecedented level of attractive interaction for hydrogen.

@@

We note that our upper bound can readily be applied to the storage of other
gasses of interest, with the proviso that the gas is far from crystallization.
Our code is available at \href{https://github.com/Jordan-Pommerenck/isothermal-gas-adsorption}{https://github.com/Jordan-Pommerenck/isothermal-gas-adsorption}.

>>>>

\startreferees{Added discussion of screening studies}
Finally, a number of empirical studies have been performed that computationally
simulate an adsorption in a vast array of possible porous
structures~\cite{firlej2013understanding, goldsmith2013theoretical,
ahmed2019exceptional}.  Such studies can guide the development of new materials
by allowing researchers to identify commonalities among materials that have
desirable properties.  However, such an approach can only place a \emph{lower
bound} on the highest attainable deliverable capacity.

@@

\startreferees{Flexible MOFs section added below}
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{figs/two-phase}
    \caption{Cartoon of a two-phase, collapsing material. The material can exist in two phases: an open phase in which gas molecules can adsorb, and a closed phase that is collapsed and cannot fit any gas molecules. Take the closed phase as more stable, so that the material can collapse and expel residual gas.
    The pressure of gas at which the structural transition occurs depends on the gas-host interactions and relative stability of the phases. We wish for the structural transition to occur between $\pfull$ and $\pempty$.
    }
    \label{fig:flexible-cartoon}
\end{figure}

@@

       comparison~\cite{mason2015methane}, along with the free energy difference between open and closed conformations~\cite{mason2015methane, choi2008broadly}.}

@@

Figure~\ref{fig:methane-flexible} illustrates
how the upper bound on the deliverable capacity of methane in a two-phase,
collapsing material depends on $\Delta F$. 
For comparison, we include the free energy
difference for Co(bdp)~\cite{choi2008broadly and its measured deliverable capacity.  
While this upper bound is not rigorous, it suggests that a two-phase flexible material for methane storage
would benefit from significantly greater stability of the closed phase---provided the open phase
had correspondingly greater attraction for the gas molecules.  Figure~\ref{fig:hydrogen-flexible}
shows the corresponding result for hydrogen storage, indicating that, for a flexible material to
reach the DOE ULTIMATE deliverable capacity, it would require far greater stability for the closed
phase, as well as an unprecedented level of attractive interaction for hydrogen.

@@

We note that our upper bound can readily be applied to the storage of other
gasses of interest, with the proviso that the gas is far from crystallization.
Our code is available at \href{https://https://github.com/droundy/thesis-pommerenck/tree/master/gas-adsorption}{https://https://github.com/droundy/thesis-pommerenck/tree/master/gas-adsorption}.
